---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# B2Prebake

<!-- badges: start -->
<!-- badges: end -->

The goal of B2Prebake is to provide a function ('count_all_missing_by_group') to simplify counting missing values for all columns of a data frame by group.

## Installation

Ensure devtools is installed. If not installed, run install.packages("devtools") to install it. You can install the development version of the B2Prebake package like so:

``` r
devtools::install_github("stat545ubc-2023/B2Prebake")
```

## Example
```{r load packages}
library(B2Prebake)
library(dplyr) #load relevant packages
```
'count_all_missing_by_group' can compute the number of missing values in the 'small_tbl' tibble grouped by the `group` variable.
```{r example 1}
small_tbl <- tibble::tribble(~group,~var1,~var2,"A",1,NA,"A",2,"x","B",NA,"y","C",3,"z") # make example tibble
count_all_missing_by_group(small_tbl, group) # count_all_missing_by_group use example
```
Using the optional '.groups' argument, we can keep the output tibble grouped by the grouping column. The output tibble below remains grouped, in contrast to the output tibble above.
```{r example 2}
small_tbl <- tibble::tribble(~group,~var1,~var2,"A",1,NA,"A",2,"x","B",NA,"y","C",3,"z") # make example tibble
count_all_missing_by_group(small_tbl, group, .groups = "keep") # count_all_missing_by_group with groups retained
```

